---
title: "Farming Sytems Model Simulation in Lebung Itam and Rambai Village"
author: "Erlangga"
date: "6/30/2023"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE,error=FALSE}
library(readr)
mod <- read.csv("input_rubber_based.csv", header = TRUE, sep = ",")
knitr::kable(mod, "pipe", caption = "Input Table")
```


#### Model Function 1 (Rubber Monoculture, Rubber-areca palm-durian, Rubber-jengkol-petai, Rubber-jengkol-koetjape)
```{r echo=TRUE, warning=FALSE}
library(decisionSupport)

first_decision_function <- function(x, varnames) {
  
  # Define each variable as vectors of 25 values 
  
  # Corresponding to 25 years of simulation
  
  n_years <- 25

  # Cost Variables
  
  seedling.cost.rubber <- rep(0, n_years)
  planting.cost <- rep(0, n_years)
  land.clearing.rubber <- rep(0, n_years)
  herbicide.cost.rubber <- rep(0, n_years)
  fertilizer.cost.rubber <- rep(0, n_years)
  fertilizing.cost <- rep(0, n_years)
  harvest.cost.rubber <- rep(0, n_years)
  equipment.cost <- rep(0, n_years)
  harvesting.cost.rubber <- rep(0, n_years)
  transportation.cost.rubber <- rep(0, n_years)
  monitoring.cost.rubber <- rep(0, n_years)
  spraying.cost.rubber <- rep(0, n_years)
  
  seedling.cost.rubber.ag <- rep(0, n_years)
  harvesting.cost.rubber.ag <- rep(0, n_years)
  fertilizer.cost.rb.ag <- rep(0, n_years)
  harvesting.cost.rb.ag <- rep(0, n_years)
  harvesting.cost.rb.ag2 <- rep(0, n_years)

  seedling.cost.pn <- rep(0, n_years)
  seedling.cost.dr <- rep(0, n_years)
  
  planting.cost.chilli <- rep(0, n_years)
  harvesting.cost.chilli <- rep(0, n_years)
  planting.cost.cassava <- rep(0, n_years)
  harvesting.cost.cassava <- rep(0, n_years)
  seedling.cost.banana <- rep(0, n_years)
  planting.cost.banana <- rep(0, n_years)
  harvesting.cost.banana <- rep(0, n_years)
   
  # Benefit Variables
  
  chilli.price <- rep(0, n_years)
  chilli.yield <- rep(0, n_years)
  cassava.price <- rep(0, n_years)
  cassava.yield <- rep(0, n_years)
  banana.price <- rep(0, n_years)
  banana.yield <- rep(0, n_years)
  
  benefit.land.clearing.rubber <- rep(0, n_years)
  rubber.price <- rep(0, n_years)
  
  pt.price <- rep(0, n_years)
  jn.price <- rep(0, n_years)
  pn_yield <- rep(0, n_years)
  dr_yield <- rep(0, n_years)
  dr.price <- rep(0, n_years)
  pn.price <- rep(0, n_years)
  sn.price <- rep(0, n_years)
  sn.wood.price <- rep(0, n_years)
  sn.wood.yield <- rep(0, n_years)
  
  # Risk Variables
  
  yield.petai.risk <- rep(0, n_years)
  yield.jengkol.risk <- rep(0, n_years)
  yield.durian.risk <- rep(0, n_years)
  yield.pinang.risk <- rep(0, n_years)
  yield.rubber.risk <- rep(0, n_years)
  yield.sentul.risk <- rep(0, n_years)
  
  yield.cassava.risk <- rep(0, n_years)
  yield.chili.risk <- rep(0, n_years)
  yield.banana.risk <- rep(0, n_years)
  
  # Simulate the chance of risk events occurring during the simulation period
  
  durian.risk <- chance_event(chance = durian_risk, value_if = 1, n_years)
  pinang.risk <- chance_event(chance = pinang_risk, value_if = 1, n_years)
  rubber.risk <- chance_event(chance = rubber_risk, value_if = 1, n_years)
  petai.risk <- chance_event(chance = petai_risk, value_if = 1, n_years)
  jengkol.risk <- chance_event(chance = jengkol_risk, value_if = 1, n_years)
  sentul.risk <- chance_event(chance = sentul_risk, value_if = 1, n_years)
  
  petai.risk[1:n_years] <- vv(petai_risk, CV_risk, n_years)
  sentul.risk[1:n_years] <- vv(sentul_risk, CV_risk, n_years)
  durian.risk[1:n_years] <- vv(durian_risk, CV_risk, n_years)
  pinang.risk[1:n_years] <- vv(pinang_risk, CV_risk, n_years)
  rubber.risk[1:n_years] <- vv(rubber_risk, CV_risk, n_years)
  jengkol.risk[1:n_years] <- vv(jengkol_risk, CV_risk, n_years)
  
  yield.durian.risk[1:n_years] <- vv(yield_durian_risk, CV_risk, n_years)
  yield.pinang.risk[1:n_years] <- vv(yield_pinang_risk, CV_risk, n_years)
  yield.rubber.risk[1:n_years] <- vv(yield_rubber_risk, CV_risk, n_years)
  yield.sentul.risk[1:n_years] <- vv(yield_sentul_risk, CV_risk, n_years)
  yield.jengkol.risk[1:n_years] <- vv(yield_jengkol_risk, CV_risk, n_years)
  yield.petai.risk[1:n_years] <- vv(yield_petai_risk, CV_risk, n_years)
  
  cassava.risk <- chance_event(chance = cassava_risk, value_if = 1, n_years)
  chili.risk <- chance_event(chance = chili_risk, value_if = 1, n_years)
  banana.risk <- chance_event(chance = banana_risk, value_if = 1, n_years)
  
  cassava.risk[1:n_years] <- vv(cassava_risk, CV_risk, n_years)
  chili.risk[1:n_years] <- vv(chili_risk, CV_risk, n_years)
  banana.risk[1:n_years] <- vv(banana_risk, CV_risk, n_years)
  
  yield.cassava.risk[1:n_years] <- vv(yield_cassava_risk, CV_risk, n_years)
  yield.chili.risk[1:n_years] <- vv(yield_chili_risk, CV_risk, n_years)
  yield.banana.risk[1:n_years] <- vv(yield_banana_risk, CV_risk, n_years)
  
  # Calculate the system cost of rubber monoculture
    
  # Seedling cost rubber 
  seedling.cost.rubber[1] <- vv(seedling_cost_rubber, CV_cost, 1)
  seedling.cost.rubber[2:n_years] <- 0
  
  # Planting cost rubber 
  planting.cost[1] <- vv(planting_cost, CV_cost, 1)
  planting.cost[2:n_years] <- 0
  
  # Land clearing rubber
  land.clearing.rubber[1] <- vv(land_clearing_cost_rubber, CV_cost, 1)
  land.clearing.rubber[2:n_years] <- 0
  
  # Benefits of Land Clearing from Wood Harvesting
  benefit.land.clearing.rubber[1] <- vv(benefit_land_clearing, var_CV, 1)
  benefit.land.clearing.rubber[2:n_years] <- 0
  
  # Herbicide cost rubber
  herbicide.cost.rubber[1:n_years] <- vv(herbicide_cost_rubber, CV_cost, n_years)
  
  # Spraying cost rubber
  spraying.cost.rubber[1:n_years] <- vv(spraying_cost_rubber, CV_cost, n_years)
  
  # Fertilizer cost rubber
  fertilizer.cost.rubber[1:2] <- vv(fertilizer_cost_rubber, CV_cost, 2)
  fertilizer.cost.rubber[3:n_years] <- 0
  
  # Fertilizing cost rubber
  fertilizing.cost[1:2] <- vv(fertilizing_cost_rubber, CV_cost, 2)
  fertilizing.cost[3:n_years] <- 0
  
  # Transportation cost - monitoring the field before harvesting
  monitoring.cost.rubber[1:5] <- vv(monitoring_cost, CV_cost, 5)
  monitoring.cost.rubber[6:n_years] <- 0
  
  # Equipment cost including 3 and 5 years replacement
  equipment.cost[1] <- vv(equipment_cost_basic, CV_cost, 1)
  equipment.cost[2:5] <- 0
  equipment.cost[6] <- vv(equipment_cost_installment, CV_cost, 1)
  equipment.cost[7:9] <- 0 
  equipment.cost[10] <- vv(equipment_cost_maintenance_3, CV_cost, 1)
  equipment.cost[11] <- 0 
  equipment.cost[12] <- vv(equipment_cost_maintenance_5, CV_cost, 1)
  equipment.cost[13:15] <- 0 
  equipment.cost[16] <- vv(equipment_cost_maintenance_3, CV_cost, 1)
  equipment.cost[17] <- 0 
  equipment.cost[18] <- vv(equipment_cost_maintenance_5, CV_cost, 1)
  equipment.cost[19:21] <- 0 
  equipment.cost[22] <- vv(equipment_cost_maintenance_3, CV_cost, 1)
  equipment.cost[23:25] <- 0 
  
  # Transportation cost for harvesting rubber
  transportation.cost.rubber[1:5] <- 0
  transportation.cost.rubber[6:n_years] <- vv(transportation_cost, CV_cost, n_years - 5)
  
  # Harvesting cost rubber (including Post Harvest Treatment - sulfuric acid)
  harvest.cost.rubber[1:5] <- 0
  harvest.cost.rubber[6:n_years] <- vv(harvesting_equipment_treatment_rubber, CV_cost, n_years - 5)
  
  # Rubber price
  rubber.price[1:5] <- 0
  rubber.price[6:n_years] <- vv(rubber_price, CV_rubber_price, n_years - 5)
  
  # Sandoricum k. price
  sn.price[1:24] <- 0
  sn.price[24:n_years] <- vv(sentul_price, CV_sondrium_price, n_years - 23)
  
  # Wood Sandoricum k. price
  sn.wood.price[1:24] <- 0
  sn.wood.price[24:n_years] <- vv(wood_sentul_price, CV_sondrium_price, n_years - 23)
  
  # Wood Sandoricum k. yield
  sn.wood.yield[1:24] <- 0
  sn.wood.yield[24:n_years] <- vv(wood_sentul_yield, var_CV, n_years - 23)
  
  # Rubber yield using gompertz curve
  
  rb_yield <- gompertz_yield(max_harvest = max_rubber_harvest, 
                            time_to_first_yield_estimate = immature_rubber_est, 
                            time_to_second_yield_estimate = mature_rubber_est,
                            first_yield_estimate_percent = immature_rubber_yield_est,
                            second_yield_estimate_percent = mature_rubber_yield_est,
                            n_years = n_years, 
                            var_CV = 0, 
                            no_yield_before_first_estimate = TRUE)
  
  rb_yield_risk <- rb_yield*(1-rubber.risk*yield.rubber.risk)
  
  tot_rb_benefit <- rb_yield_risk * rubber.price
  
  
    # Parkia speciosa price
  pt.price[1:8] <- 0
  pt.price[9:n_years] <- vv(petai_price, CV_parkia_price, n_years - 8)
  
   # Archidendron jiringa price
  jn.price[1:3] <- 0
  jn.price[4:n_years] <- vv(jengkol_price, CV_archidendron_price, n_years - 3)
  
  # Harvesting cost Archidendron jiringa and Parkia speciosa
  harvesting.cost.rb.ag2[1:4] <- 0
  harvesting.cost.rb.ag2[5:n_years] <- vv(harvesting_cost_ag2, CV_cost, n_years - 4)
  
  # Archidendron jiring yield using Gompertz curve
  
  jn_yield <- gompertz_yield(max_harvest = max_jn_harvest, 
                            time_to_first_yield_estimate = immature_jn_est, 
                            time_to_second_yield_estimate = mature_jn_est,
                            first_yield_estimate_percent = immature_jn_yield_est,
                            second_yield_estimate_percent = mature_jn_yield_est,
                            n_years = n_years, 
                            var_CV = 0,
                            no_yield_before_first_estimate = TRUE)
    
  jn_yield_risk <- jn_yield*(1- jengkol.risk*yield.jengkol.risk)
  
  tot_jn_benefit <- jn_yield_risk * jn.price
  
  # Parkia speciosa yield using Gompertz curve
    
  pt_yield <- gompertz_yield(max_harvest = max_pt_harvest, 
                            time_to_first_yield_estimate = immature_pt_est, 
                            time_to_second_yield_estimate = mature_pt_est,
                            first_yield_estimate_percent = immature_pt_yield_est,
                            second_yield_estimate_percent = mature_pt_yield_est,
                            n_years = n_years, 
                            var_CV = 0, 
                            no_yield_before_first_estimate = TRUE)
  
  pt_yield_risk <- pt_yield*(1-petai.risk*yield.petai.risk)
  
  tot_pt_benefit <- pt_yield_risk * pt.price
  
   # Sandoricum k. yield at the end of life cycle (wood)
  
  sn_yield <- gompertz_yield(max_harvest = max_sn_harvest, 
                            time_to_first_yield_estimate = immature_sn_est, 
                            time_to_second_yield_estimate = mature_sn_est,
                            first_yield_estimate_percent = immature_sn_yield_est,
                            second_yield_estimate_percent = mature_sn_yield_est,
                            n_years = n_years, 
                            var_CV = 0, 
                            no_yield_before_first_estimate = TRUE)
  
  sn_yield_risk <- sentul_yield*(1-sentul.risk*yield.sentul.risk)
  
  tot_sn_benefit <- (sn_yield_risk * sn.price) + (sn.wood.yield * sn.wood.price)
  
  # Benefits of rubber using Gompertz curve 
  rb_yield <- gompertz_yield(max_harvest = max_rubber_harvest, 
                            time_to_first_yield_estimate = immature_rubber_est, 
                            time_to_second_yield_estimate = mature_rubber_est,
                            first_yield_estimate_percent = immature_rubber_yield_est,
                            second_yield_estimate_percent = mature_rubber_yield_est,
                            n_years = n_years, 
                            var_CV = 0, 
                            no_yield_before_first_estimate = TRUE)
  
  rb_yield_risk <- rb_yield*(1-rubber.risk*yield.rubber.risk)
  
  tot_rb_benefit <- rb_yield_risk * rubber.price
  
  
  # Chili and Cassava at first year, Banana at the second year of system
  
  chilli.yield[1] <- vv(chilli_yield, var_CV, 1)
  chilli.yield[2:n_years] <- 0
  
  chilli.price[1] <- vv(chilli_price, CV_chili_price, 1)
  chilli.price[2:n_years] <- 0
  
  planting.cost.chilli[1] <- vv(planting_cost_chilli, CV_cost, 1)
  planting.cost.chilli[2:n_years] <- 0
  
  harvesting.cost.chilli[1] <- vv(harvesting_cost_chilli, CV_cost, 1)
  harvesting.cost.chilli[2:n_years] <- 0
  
  planting.cost.cassava[1] <- vv(planting_cost_cassava, CV_cost, 1)
  planting.cost.cassava[2:n_years] <- 0
  
  harvesting.cost.cassava[1] <- vv(harvesting_cost_cassava, CV_cost, 1)
  harvesting.cost.cassava[2:n_years] <- 0
  
  cassava.price[1] <- vv(cassava_price, CV_cassava_price, 1)
  cassava.price[2:n_years] <- 0
  
  cassava.yield[1] <- vv(cassava_yield, var_CV, 1)
  cassava.yield[2:n_years] <- 0
  
  seedling.cost.banana <- vv(seedling_cost_banana, CV_cost, 1)
  seedling.cost.banana[2:n_years] <- 0
  
  planting.cost.banana[1] <- 0
  planting.cost.banana[2] <- vv(planting_cost_banana, CV_cost, 1)
  planting.cost.banana[3:n_years] <- 0
  
  harvesting.cost.banana[1] <- 0
  harvesting.cost.banana[2] <- vv(harvesting_cost_banana, CV_cost, 1)
  harvesting.cost.banana[3:n_years] <- 0
  
  banana.yield[1] <- 0
  banana.yield[2] <- vv(banana_yield, var_CV, 1)
  banana.yield[3:n_years] <- 0
  
  banana.price[1] <- 0
  banana.price[2] <- vv(banana_price, CV_banana_price, 1)
  banana.price[3:n_years] <- 0
  
  
  chili_yield_risk <-  chilli.yield*(1- chili.risk*yield.chili.risk)

  tot_chilli_benefit <- (chili_yield_risk* chilli.price) - planting.cost.chilli - harvesting.cost.chilli
                           
  cassava_yield_risk <- cassava_yield * (1- cassava.risk*yield.cassava.risk)
  
  tot_cassava_benefit <-  (cassava_yield_risk * cassava.price) - planting.cost.cassava - harvesting.cost.cassava
  
  banana_yield_risk <- banana.yield * (1- banana.risk*yield.banana.risk) 
  
  tot_banana_benefit <- (banana_yield_risk * banana.price) - seedling.cost.banana - planting.cost.banana - harvesting.cost.banana
  
  
  tot_chilli_benefit.efl <- (chilli.yield*(1- chili.risk*yield.chili.risk)) * chilli.price
  
  tot_cassava_benefit.efl <- (cassava.yield * (1- cassava.risk*yield.cassava.risk)) * cassava.price
  
  tot_banana_benefit.efl <- ((banana.yield * (1- banana.risk*yield.banana.risk)) * banana.price) - seedling.cost.banana
  
  # Calculate Rubber agroforestry
  
  # The different between agroforestry (Areca c. and Durio z.) and monoculture are only seedling quantity and fertilizer quantity.
      
  # Seedling cost rubber agroforestry 
  
  seedling.cost.rubber[1] <- vv(seedling_cost_rubber_ag, CV_cost, 1)
  seedling.cost.rubber[2:n_years] <- 0
  
  # Fertilizer cost rubber
  fertilizer.cost.rb.ag[1:2] <- vv(fertilizer_cost_rb_ag, CV_cost, 2)
  fertilizer.cost.rb.ag[3:n_years] <- 0

  # Harvesting cost (Areca catechu and Durio zibethinus)
  
  harvesting.cost.rb.ag[1:3] <- 0
  harvesting.cost.rb.ag[4:n_years] <- vv(harvesting_cost_ag, CV_cost, n_years - 3)  
  
  # Durian price
  dr.price[1:8] <- 0
  dr.price[9:n_years] <- vv(durian_price, CV_durian_price, n_years - 8)
  
  # Areca nut (pinang) price
  pn.price[1:3] <- 0
  pn.price[4:n_years] <- vv(pinang_price, CV_areca_price, n_years - 3)
  
  # Benefits of rubber agroforestry type 1
  rb_ag_yield <- gompertz_yield(max_harvest = max_rubber_ag_harvest, 
                            time_to_first_yield_estimate = immature_rubber_est, 
                            time_to_second_yield_estimate = mature_rubber_est,
                            first_yield_estimate_percent = immature_rubber_yield_est,
                            second_yield_estimate_percent = mature_rubber_yield_est,
                            n_years = n_years, 
                            var_CV = 0, 
                            no_yield_before_first_estimate = TRUE)
  
  rb_ag_yield_risk <- rb_ag_yield*(1-rubber.risk*yield.rubber.risk)
  
  tot_rb_ag_benefit <- rb_ag_yield_risk * rubber.price
  
  # Durian Yield 
  
  dr_yield <- gompertz_yield(max_harvest = max_dr_harvest, 
                            time_to_first_yield_estimate = immature_dr_est, 
                            time_to_second_yield_estimate = mature_dr_est,
                            first_yield_estimate_percent = immature_dr_yield_est,
                            second_yield_estimate_percent = mature_dr_yield_est,
                            n_years = n_years, 
                            var_CV = 0,
                            no_yield_before_first_estimate = TRUE)
    
  dr_yield_risk <- dr_yield*(1- durian.risk*yield.durian.risk)
  
  tot_dr_benefit <- dr_yield_risk * dr.price
  
  # Areca nut (pinang) yield
    
  pn_yield <- gompertz_yield(max_harvest = max_pn_harvest, 
                            time_to_first_yield_estimate = immature_pn_est, 
                            time_to_second_yield_estimate = mature_pn_est,
                            first_yield_estimate_percent = immature_pn_yield_est,
                            second_yield_estimate_percent = mature_pn_yield_est,
                            n_years = n_years, 
                            var_CV = 0, 
                            no_yield_before_first_estimate = TRUE)
  
  pn_yield_risk <- pn_yield*(1-pinang.risk*yield.pinang.risk)
  
  tot_pn_benefit <- pn_yield_risk * pn.price
  
  
  # Calculate the NPV of rubber system
    
  total_rb_benefit.efl <- (tot_rb_benefit + benefit.land.clearing.rubber - seedling.cost.rubber - 
                           land.clearing.rubber - fertilizer.cost.rubber - equipment.cost - 
                           harvest.cost.rubber - transportation.cost.rubber - herbicide.cost.rubber +
                           tot_banana_benefit.efl + tot_cassava_benefit.efl + tot_chilli_benefit.efl)/cur_change
  
  # Calculate NPV Rubber-Areca catechu and Durio zibethinus (excluding family labour calculation)
   
  total_rb_ag_benefit.efl <- ((tot_rb_ag_benefit + benefit.land.clearing.rubber + tot_dr_benefit + 
                               tot_pn_benefit) - seedling.cost.rubber - land.clearing.rubber - 
                               monitoring.cost.rubber - transportation.cost.rubber - fertilizer.cost.rubber - 
                               equipment.cost - harvest.cost.rubber)/cur_change
  
  
  # Benefit Rubber-Archidendron jiring and Parkia speciosa (excluding family labour calculation)

  total_rb_ag2_benefit.efl <- (tot_rb_benefit + benefit.land.clearing.rubber + tot_pt_benefit + tot_jn_benefit 
                           - seedling.cost.rubber - land.clearing.rubber - fertilizer.cost.rubber 
                           - equipment.cost - harvest.cost.rubber - herbicide.cost.rubber 
                           - monitoring.cost.rubber - transportation.cost.rubber
                           + tot_banana_benefit.efl + tot_cassava_benefit.efl + tot_chilli_benefit.efl)/cur_change
  
  # Total benefit Rubber-Archidendron jiring - Sondrium k. (excluding family labour calculation)

  total_rb_ag3_benefit.efl <- (tot_rb_benefit + benefit.land.clearing.rubber + tot_sn_benefit + tot_jn_benefit - 
                              seedling.cost.rubber - land.clearing.rubber - fertilizer.cost.rubber - 
                              equipment.cost - harvest.cost.rubber - herbicide.cost.rubber -
                              monitoring.cost.rubber - transportation.cost.rubber +
                              tot_banana_benefit.efl + tot_cassava_benefit.efl + tot_chilli_benefit.efl)/cur_change
  
  # NPV of comparison
  
  NPV_rb.efl <- discount(total_rb_benefit.efl, discount_rate = discount_rate, calculate_NPV = TRUE)
  
  NPV_rb_ag.efl <- discount(total_rb_ag_benefit.efl, discount_rate = discount_rate, calculate_NPV = TRUE)
  
  NPV_rb_ag2.efl <- discount(total_rb_ag2_benefit.efl, discount_rate = discount_rate, calculate_NPV = TRUE)
  
  NPV_rb_ag3.efl <- discount(total_rb_ag3_benefit.efl, discount_rate = discount_rate, calculate_NPV = TRUE)
  
  # Benefit of choosing rubber-Areca catechu and Durio zibethinus over rubber monoculture (excluding family labour calculation)

  tradeoff_FL <- NPV_rb_ag.efl - NPV_rb.efl
  
  #  Benefit of choosing Rubber-Archidendron jiring and Parkia speciosa over rubber monoculture (excluding family labour calculation)
  
  tradeoff_FL2 <- NPV_rb_ag2.efl - NPV_rb.efl
  
  # Benefit of choosing Rubber-Archidendron j. - Sondrium k. over rubber monoculture (excluding family labour calculation)
  
  tradeoff_FL3 <- NPV_rb_ag3.efl - NPV_rb.efl
  
  # Final NPV of the decision to choose
  
  NPV_tradeoff_FL1 <- discount(tradeoff_FL, discount_rate = discount_rate, calculate_NPV = TRUE)

  NPV_tradeoff_FL2 <- discount(tradeoff_FL2, discount_rate = discount_rate, calculate_NPV = TRUE)
  
  NPV_tradeoff_FL3 <- discount(tradeoff_FL3, discount_rate = discount_rate, calculate_NPV = TRUE)
  
  # In the return list, one can indicate any outcome they wish to see from the model
  return(list(trade_off_FL1 = NPV_tradeoff_FL1,
              trade_off_FL2 = NPV_tradeoff_FL2,
              trade_off_FL3 = NPV_tradeoff_FL3,
              rb_ag.efl_NPV = NPV_rb_ag.efl,
              rb_ag2.efl_NPV = NPV_rb_ag2.efl,
              rb_ag3.efl_NPV = NPV_rb_ag3.efl,
              rb.efl_NPV = NPV_rb.efl,
              Cash_Flow_Rubber_Excl_FL = total_rb_benefit.efl,
              Cash_Flow_Rubber_Pinang_Durian_Excl_FL = total_rb_ag_benefit.efl,
              Cash_Flow_Rubber_Petai_Jengkol_Excl_FL = total_rb_ag2_benefit.efl,
              Cash_Flow_Rubber_Jengkol_Sentul_Excl_FL = total_rb_ag3_benefit.efl))
}

```


## Monte Carlo Simulation

After the model function has been created, it is continued to the function "mCSimulation" from the decision Support Package. The simulation is run a total of 10000 times.

```{r}
library(decisionSupport)

# Read the estimates from the CSV file
estimate <- estimate_read_csv("input_rubber_based.csv")

# Perform the Monte Carlo simulation Model 1
mcSimulation_result1 <- mcSimulation(estimate = estimate,
                                     model_function = first_decision_function,
                                     numberOfModelRuns = 10000,
                                     functionSyntax = "plainNames")

```


## Cashflow


### Plot cash flow Rubber-Areca catechu and Durio zibethinus (Cash flow 1)
```{r echo=TRUE, warning=FALSE, fig.cap="**Graph. 1 Cashflow Rubber-Areca palm-Durian (Excluding Family Labour Calculation)**",}
plot_cashflow(mcSimulation_object = mcSimulation_result1,
                        color_25_75 = "honeydew3",
                        color_5_95 = "honeydew2",
                        color_median = "blue",
                        cashflow_var_name = "Cash_Flow_Rubber_Pinang_Durian_Excl_FL")
```


### Plot cash flow Rubber-jengkol-petai

```{r echo=TRUE, fig.cap="**Graph. 2. Cash flow Rubber-jengkol-petai (Excluding Family Labour Calculation)**",}
plot_cashflow(mcSimulation_object = mcSimulation_result1,
                        color_25_75 = "bisque2",
                        color_5_95 = "bisque",
                        color_median = "blue",
                        cashflow_var_name = "Cash_Flow_Rubber_Petai_Jengkol_Excl_FL")
```


### Plot cash flow Rubber-jengkol-koetjape

```{r echo=TRUE, warning=FALSE, fig.cap="**Graph. 3. Cash flow Rubber-jengkol-koetjape (Excluding Family Labour Calculation)**",}
plot_cashflow(mcSimulation_object = mcSimulation_result1,
                        color_25_75 = "plum",
                        color_5_95 = "plum1",
                        color_median = "blue",
                        cashflow_var_name = "Cash_Flow_Rubber_Jengkol_Sentul_Excl_FL")
```


### Plot cash flow Rubber Monoculture

```{r echo=TRUE, warning=FALSE, fig.cap="**Graph. 4. Cash flow Rubber Monoculture (Excluding Family Labour Calculation)**",}
plot_cashflow(mcSimulation_object = mcSimulation_result1,
              color_25_75 = "yellow3",
              color_5_95 = "khaki",
              color_median = "blue",
              cashflow_var_name = "Cash_Flow_Rubber_Excl_FL")
```

## NPV Comparisson

```{r echo=TRUE, warning=FALSE, fig.cap="**Graph. 5. NPV Comparison Rubber-based agroforestry over Rubber Monoculture**",}
decisionSupport::plot_distributions(mcSimulation_object = mcSimulation_result1, 
                                    vars = c("rb.efl_NPV", "rb_ag.efl_NPV", "rb_ag2.efl_NPV", "rb_ag3.efl_NPV"),
                                    method = 'smooth_simple_overlay', 
                                    bins = 150,
                                    old_names = NULL,
                                    new_names = NULL,
                                    colors = c("darkolivegreen2", "darkorange3", "springgreen4","mediumorchid2" ),
                                    outlier_shape = ".",
                                    x_axis_name = "Outcome distribution",
                                    y_axis_name = "frequency",
                                    base_size = 11)
```

### Trade off Rubber-based agroforestry over Rubber Monoculture
```{r echo=TRUE, warning=FALSE, fig.cap="**Graph. 8. Tradeoff Rubber-based agroforestry over Rubber Monoculture**",}
decisionSupport::plot_distributions(mcSimulation_object = mcSimulation_result1, 
                                    vars = c("trade_off_FL1","trade_off_FL2","trade_off_FL3"),
                                    method = 'boxplot',
                                    colors = c("goldenrod1","aquamarine3", "plum3"),
                                    outlier_shape = 3)
```
